MS&E 226: Project Part 1 Code

### 2024-12-04 MS&E 226_Project Part 2_Code.Rmd
final edits

# Print significant coefficients
print(significant_coefficients)

@@

# Print significant coefficients from the subset model
print(significant_subset_coefficients)
```

>>>>

significant_coefficients_df <- data.frame(
  Variable = rownames(significant_coefficients),
  Pr_greater_than_t = significant_coefficients[, 4]
)

# Print the table
print(significant_coefficients_df)

@@

significant_subset_coefficients_df <- data.frame(
  Variable = rownames(significant_subset_coefficients),
  Pr_greater_than_t = significant_subset_coefficients[, 4]
)

# Print the table
print(significant_subset_coefficients_df)
```
